Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-02-04 paper.qmd
Updated Figure 7

sc_ltr_pos <- c(0.08, 0.9)
# sc_xlims <- c(-0.5, 1.47)
# sc_ylims <- c(-0.32, 2.1)
sc_xlims <- c(-0.3, 1.2)
sc_ylims <- c(-0.17, 1.2)

@@

hex_grid_coloured_two_curvy2 <- ggplot() + 
  geom_polygon(
    data = hex_grid_with_counts_two_curvy2, 
    aes(x = x, y = y, 
        group = hex_poly_id, 
        fill = std_counts), 
        color = "grey70", 
        linewidth=0.2) +
  geom_point(data = tsne_two_curvy_scaled,
           aes(x = tSNE1, y = tSNE2),
           alpha = 0.3,
           size = 0.5) +
  scale_fill_viridis_c(direction = -1, 
    na.value = "#ffffff", option = "C") +
  xlim(c(-0.3, 1.2)) + ylim(c(-0.17, 1.1)) +
  interior_annotation("a", sc_ltr_pos)

@@

hex_grid_coloured_two_curvy3 <-  ggplot() + 
  geom_polygon(
    data = hex_grid_with_counts_s_curve3, 
    aes(x = x, y = y, 
        group = hex_poly_id, 
        fill = std_counts), 
        color = "grey70", linewidth=0.2) +
  geom_point(data = tsne_two_curvy_scaled,
           aes(x = tSNE1, y = tSNE2),
           alpha = 0.3,
           size = 0.5) +
  scale_fill_viridis_c(direction = -1, na.value = "#ffffff", option = "D") +
  xlim(c(-0.3, 1.2)) + ylim(c(-0.17, 1.1)) +
  interior_annotation("c", sc_ltr_pos)
```

>>>>

sc_ltr_pos <- c(0.08, 0.9)
# sc_xlims <- c(-0.5, 1.47)
# sc_ylims <- c(-0.32, 2.1)
sc_xlims <- c(-0.3, 1.2)
sc_ylims <- c(-0.17, 1.25)

@@

hex_grid_coloured_two_curvy2 <- ggplot() + 
  geom_polygon(
    data = hex_grid_with_counts_two_curvy2, 
    aes(x = x, y = y, 
        group = hex_poly_id, 
        fill = std_counts), 
        color = "grey70", 
        linewidth=0.2) +
  geom_point(data = tsne_two_curvy_scaled,
           aes(x = tSNE1, y = tSNE2),
           alpha = 0.3,
           size = 0.5) +
  scale_fill_viridis_c(direction = -1, 
    na.value = "#ffffff", option = "C") +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("a", sc_ltr_pos)

@@

hex_grid_coloured_two_curvy3 <-  ggplot() + 
  geom_polygon(
    data = hex_grid_with_counts_s_curve3, 
    aes(x = x, y = y, 
        group = hex_poly_id, 
        fill = std_counts), 
        color = "grey70", linewidth=0.2) +
  geom_point(data = tsne_two_curvy_scaled,
           aes(x = tSNE1, y = tSNE2),
           alpha = 0.3,
           size = 0.5) +
  scale_fill_viridis_c(direction = -1, na.value = "#ffffff", option = "D") +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("c", sc_ltr_pos)
```
